New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2022-12-01 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd
update fitbit paper

The sample consisted in total of *N* = `r length(df_demo_all$ID)` pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding demographic data from *N* = `r length(df_demo$ID)` subjects.

@@

### Teachers' self-assessment of arousal during the teaching phase

>>>>

The sample consisted in total of *N* = `r length(df_demo_all$ID)` pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from *N* = `r length(df_demo$ID)` subjects.

@@

### Teachers' self-assessment of arousal during the teaching phase
The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson. For this purpose, two numerical 11-point rating scales were used: _(1)_	The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: "On a scale of 0-10: how disruptive did you find the event? 0 is not disruptive at all, 10 is extremely disruptive" _(2)_	The second rating scale assessed the teacher’s subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: "How confident did you feel in dealing with this event on a scale of 0-10? 0 is not confident at all and 10 is extremely confident"
The response format was purposely chosen to be closed and with several answer options in order to assign numerical values to the subjetcts' self-assessment and emotional experience, and thus to make them measurable and comparable [@eid2015statistik; @doring2016empirische]. The gradations of the rating scale were unambiguous and the intervals between them identical. The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally to the experimenter.

### 2022-12-01 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
update fitbit paper

@@

@@

The heart rate of each subject were measured before, during and after the experiment.

\hypertarget{steps}{%
\subsubsection{Steps}\label{steps}}

Using the FitBit we measured the steps a person walked during the experiment as well. We validated the steps in six randomly selected videos by manual step counting. A step was considered to be the movement of the subject's foot forward, backward, or sideways. The measurement was not as reliable as hoped.

@@

>>>>

The subject's self-assessment of arousal in response to the nine disruptions during the lesson was assessed in a Stimulated Recall Interview that took place after the lesson.

For this purpose, two numerical 11-point rating scales were used:
(1) The first rating scale collected data of the teacher's subjective perception of disruptiveness of each disruption with the following question: ``On a scale of 0-10: how disruptive did you find the event? 0 is not disruptive at all, 10 is extremely disruptive''
(2) The second rating scale assessed the teacher's subjective perception of confidence in dealing with the disruptions during the lesson asked as follows: ``How confident did you feel in dealing with this event on a scale of 0-10? 0 is not confident at all and 10 is extremely confident''

The response format here was purposely chosen to be closed and with several answer options in order to assign numerical values to the assessment and emotional experience of the subjects, and thus to make them measurable and comparable {[}Eid, Gollwitzer, and Schmitt (2015); doring2016empirische{]}. The gradations of the rating scale are unambiguous and the intervals between them are identical. The characteristic value was estimated by the subjects immediately after seeing the recording of the respective disruption and communicated verbally.

@@

The data collection was part of a larger research project with a planned sample of \emph{n} = 40 in-service teachers and \emph{n} = 40 pre-service teachers.

In a controlled laboratory setting, heart rate data in beats per minute (bpm) were recorded using Fitbit Charge 4 over a total period of approximately two hours. Within this time frame, teachers taught a 15-minute self-prepared lesson to an audience of three actors. For analyzing the heart rate data, we selected five 10-minute intervals of theoretical interest:
(1) the pre-teaching phase, which started from the moment the subject put on the watch
(2) the teaching phase, which began at the moment when the subject started the lesson
(3) the post-teaching phase, which was the 10 minutes immediately after the end of the lesson
(4) the interview phase, which was 10 minutes in the middle of the interview (for this, the difference was calculated from the end of the lesson and from the time when the subject took off the watch. This duration was divided in two to get to the middle of the interval and 5 minutes were subtracted to get to the start of the 10-minute interval),
(5) the end phase, which was the 10 minutes before the subject took off the watch.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-eid2015statistik}{}}%
Eid, M., Gollwitzer, M., \& Schmitt, M. (2015). \emph{Statistik und forschungsmethoden: Mit online-materialien (4., {ü}berarb. Und erw. aufl.)}. Weinheim: Beltz. Retrieved from https://contentselect. com/media/moz\_viewer~\ldots.
